Reducing RES Droughts through the integration of wind and PV

### 2024-11-28 Article/main.tex
Add some changes

\noindent As the share of renewable energy sources (RES) like wind and photovoltaic (PV) power grows, their dependence on weather poses a critical challenge for energy systems. This study investigates periods of low renewable generation, known as RES droughts, focusing on Ireland's current wind-dominated energy mix and a projected scenario with a more balanced distribution of wind and PV capacity. Three different modelled datasets are used, and their capacity factors are compared to observed data to quantify their overall skill. Then, using a RES drought definition with a fixed threshold, their skill at representing these events is assessed. These modelled capacity factors allow for an expansion over a 45-year period, allowing for an analysis of the frequency, duration and return periods of RES droughts at a climatological scale. Results show the importance of model selection for RES drought risk assessment. On a similar note, the addition of PV capacity to a wind-dominated system results in a large reduction in the frequency and duration of RES droughts, with a more balanced energy mix minimising seasonal drought patterns. These findings underscore the importance of diversification in RES capacity to enhance energy security and resilience. \textcolor{magenta}{I rewrote this and I still do not like it}

>>>>

\noindent As the share of renewable energy sources (RES) like wind and photovoltaic (PV) power grows, their dependence on weather poses a critical challenge for energy systems. This study investigates periods of low renewable generation, known as RES droughts, with a focus on Ireland, its current wind-dominated energy mix and the more balanced target distribution of wind and PV capacity. Three different models are used to estimate the capacity factors of the different scenarios, and their overall skill is quantified by comparing them to observed data. Their skill at representing RES droughts is also calculated by using a RES drought definition with a fixed threshold. These models allow for an expansion of the capacity factor series over a 45-year period, provide the opportunity for an analysis of the frequency, duration and return periods of RES droughts at a climatological scale, identifying risks that may not be explicit at the short observed time scales. Results show the importance of model selection for RES drought risk assessment. On a similar note, the addition of PV capacity to a wind-dominated system results in a large reduction in the frequency and duration of RES droughts, with a more balanced energy mix minimising seasonal drought patterns. These findings underscore the importance of diversification in RES capacity to enhance energy security and resilience. \textcolor{magenta}{I rewrote this and I still do not like it}
